---
title: "Training, Templates and Tutorials"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
    includes:
      before_body: [includes/include_header.html, includes/include_header_navpage.html]
editor_options: 
  chunk_output_type: console
---

```{r, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

<link href="https://use.fontawesome.com/releases/v5.0.6/css/all.css" rel="stylesheet">

**OxShef: dataviz** splits our documentation over multiple websites, this page combines a high-level overview of all the things you need to know from these sites in order to design effective visualisations as part of a reproducible dataviz workflow.

<div class='row'>

<div class='col-sm-4'>

<center><h5>[**OxShef: Charts**](https://charts.oxshef.io)</h5></center>
<center><i class='fas fa-chart-area fa-2x'></i></center>
- **OxShef: Charts** provides advice on how to select the most appropriate charts for your data and how to avoid common mistakes when visualising data.

</div>

<div class='col-sm-4'>

<center><h5>[**OxShef: Tools**](https://tools.oxshef.io)</h5></center>
<center><i class='fas fa-wrench fa-2x'></i></center>
- **OxShef: Tools** provides advice on choosing data visualisations tools that [support a reproducible dataviz workflow](http://oxshef-tools.netlify.com/reproducible-dataviz-workflow.html).
- **OxShef: Tools** maintains an overview of [popular data visualisation tools](http://oxshef-tools.netlify.com/list-of-tools.html) and dedicated websites for select technologies which fully support accessing data from DOI-issuing repositories.
</div>

<div class='col-sm-4'>

<center><h5>[**OxShef: Publishers**](http://publishers.oxshef.io)</h5></center>
<center><i class='fas fa-file-pdf fa-2x'></i></center>
- **OxShef: Publishers** provides advice on choosing publishers that [support embedding visualisations alongside publications](http://oxshef-publishers.netlify.com/publishers-list.html).
- **OxShef: Publishers** also maintains an overview of [data repositories](http://oxshef-publishers.netlify.com/data-repositories-list.html) and their suitability for a reproducible dataviz workflow

</div>

</div>

```{r}
publishers_training_tutorials_and_templates <- tempfile(fileext = ".Rmd")
download.file("https://raw.githubusercontent.com/OxShef/oxshef_publishers/master/training-tutorials-and-templates.Rmd", publishers_training_tutorials_and_templates)
```


```{r, echo=FALSE, results='hide'}
tools_training_tutorials_and_templates <- tempfile(fileext = ".Rmd")
download.file("https://raw.githubusercontent.com/OxShef/oxshef_tools/master/training-tutorials-and-templates.Rmd", tools_training_tutorials_and_templates)
```

```{r}
# setInternet2(use = TRUE)
library("tidyverse")
library("readxl")
download.file("https://raw.githubusercontent.com/OxShef/oxshef_charts/master/training-tutorials-and-templates.Rmd", "training-tutorials-and-templates.Rmd")

download.file("https://raw.githubusercontent.com/OxShef/oxshef_charts/master/oxshef-viz-tutorials-etc.xlsx", "oxshef-viz-tutorials-etc.xlsx")

viz_tutorial_logos <- read_xlsx("oxshef-viz-tutorials-etc.xlsx") %>%
  select(image.path) %>%
  filter(!is.na(image.path)) %>%
  .[[1]]

add_viz_tutorial_logo <- function(logo) {
  download.file(url = file.path(
  "https://raw.githubusercontent.com/OxShef/oxshef_charts/master/images/table-of-viz-tutorials-etc",
  logo
  ),
  destfile = file.path("images/table-of-viz-tutorials-etc", logo))
}

viz_tutorial_logos %>%
  walk(add_viz_tutorial_logo)

download.file("https://raw.githubusercontent.com/OxShef/oxshef_charts/master/images/revision-pie.png",
              "images/revision-pie.png")

```

<hr>

# Reproducability and working with publishers

```{r child = publishers_training_tutorials_and_templates}
```

<hr>

# Advice on dataviz tool selection

```{r child = tools_training_tutorials_and_templates}
```

<hr>

# Advice on charts

```{r child = "training-tutorials-and-templates.Rmd"}
```

